% !TeX program = xelatex
% !TeX encoding = UTF-8

\documentclass[xcolor=table,dvipsnames,svgnames,aspectratio=169]{beamer}

\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{array}
\usepackage{tabularx}
\usepackage{colortbl}

\graphicspath{{figures/}}

\usetheme[min,blue]{sjtubeamer}
\titlegraphic{}

\title[Envoix · Project Proposal]%
  {\textbf{Envoix}: A Hybrid Adaptive Platform for Secure End-to-End File Transfer}
\subtitle{VE441 · App Development for Entrepreneurs · Project Proposal}
\author{Sun Qizhen \and Zhang Jinbin \and Li Yuhao \and He Yumeng}
\institute[SJTU GC]{Shanghai Jiao Tong University Global College}
\date{\today}

\begin{document}

\maketitle

% ----------------------------------------------------------------
% Elevator Pitch
% ----------------------------------------------------------------
\begin{frame}{Envoix --- Elevator Pitch}
  \begin{block}{}
    \centering\large\itshape
    Never waste time choosing how to send a file again ---\\
    Envoix automatically selects the fastest, most secure transfer path\\
    across any platform and any network.
  \end{block}

  \vspace{1.5em}

  \begin{itemize}\setlength{\itemsep}{0.55em}
    \item \textbf{Zero decision cost} --- routing is automatic, zero manual selection
    \item \textbf{Uniform E2EE} --- all transfer modes, all files, always encrypted
    \item \textbf{Encrypted chat} --- conversation context stays as private as the file
    \item \textbf{No account required} --- pair instantly via QR code or short token
  \end{itemize}
\end{frame}

% ----------------------------------------------------------------
% Table of Contents
% ----------------------------------------------------------------
\begin{frame}{Outline}
  \tableofcontents[hideallsubsections]
\end{frame}

\AtBeginSection[]{
  \begin{frame}
    \tableofcontents[currentsection,subsectionstyle=show/show/hide]
  \end{frame}
}

% ================================================================
\section{Team Members}
% ================================================================

\begin{frame}{Team Members \quad{\small\normalfont\textbf{Team:} NUUB \enspace \textbf{PM:} Zhang Jinbin}}

\vspace{-0.3em}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\textwidth}{@{} >{\bfseries}l l X X @{}}
  \toprule
  Name & jAccount & Task Assignment & Technical Strengths \\
  \midrule
  Sun Qizhen   & qz\_sun       & Product architecture, routing engine, network path scoring & Networking, distributed systems, system design \\
  Zhang Jinbin & moranxuege   & PM, mobile client (Android/iOS), cross-platform UI/UX & Android (Kotlin), iOS (Swift), UX implementation \\
  Li Yuhao     & 17521218310  & End-to-end encryption, QR/token handshake, encrypted chat & Cryptography, backend security, protocol design \\
  He Yumeng    & y4954he      & Relay server, deployment, testing & Backend, QA, Rust REST \\
  \bottomrule
\end{tabularx}

\end{frame}

% ================================================================
\section{Customer Profile}
 
\begin{frame}{Affinity Map}
  \vfill
  \centering
  {\LARGE\faLink}\\[1.2em]
  \href{https://chkxw.github.io/affinity-map-site/}%
       {\large\ttfamily chkxw.github.io/affinity-map-site}
  \vfill
\end{frame}
 
% ---- Customer profile slide 1: context ----
\begin{frame}[shrink=16, t]{Customer Profile --- Who Are Our Users?}
  \begin{columns}[T]
    \column{0.48\textwidth}
    \begin{block}{User Context (17 interviews)}
      \begin{itemize}
        \item Own \textbf{2--3 devices}: phone + laptop (± tablet)
        \item Platforms span \textbf{iOS, Android, Windows, macOS, Linux}
        \item \textbf{8 / 17} transfers are self-to-self between own devices
        \item Files: art / photos, coursework docs, large datasets
      \end{itemize}
    \end{block}
    \vspace{0.1em}
    \begin{block}{Current Tools}
      \small
      \begin{tabular}{@{}ll@{}}
        WeChat File Transfer  & universal default (10 / 17) \\
        Google Drive          & large files                 \\
        Discord / QQ          & makeshift shuttles          \\
        USB cable / drive     & offline fallback            \\
      \end{tabular}
    \end{block}
    \column{0.48\textwidth}
    \begin{alertblock}{Key Insight}
      Tool choice is driven by \textbf{habit, not quality}.
      \vspace{0.4em}
 
      \small\itshape
      ``WeChat was already open, so I just used it.
       I wasn't thinking about AirDrop.''
      \vspace{0.4em}
 
      \normalfont\small
      Even full Apple-ecosystem users prefer WeChat
      over AirDrop due to inertia.
    \end{alertblock}
    \vspace{0.5em}
    \begin{block}{What They Like Today}
      \small
      \begin{itemize}
        \item \textbf{Always there} --- no extra install needed
        \item \textbf{Persistent storage} --- QQ files don't expire
        \item \textbf{Multi-purpose} --- chat + transfer in one app
      \end{itemize}
    \end{block}
  \end{columns}
\end{frame}
 
% ---- Customer profile slide 2: pain points ----
\begin{frame}[shrink=8]{Customer Profile --- Key Pain Points}
  \small
  \renewcommand{\arraystretch}{1.2}
  \noindent\hspace*{-0.5cm}%
  \begin{tabularx}{\dimexpr\textwidth+0.5cm\relax}{@{} p{3.6cm} X @{}}
    \toprule
    \textbf{Pain Point} & \textbf{Representative Quote} \\
    \midrule
    Transfer interrupted; no auto-resume (\texttimes\,11)
      & \small\itshape ``scp cut out halfway and I had to start over from the beginning'' \\
    \rowcolor{cprimary!8}
    Cross-platform wall: multi-step detour (\texttimes\,7)
      & \small\itshape ``I had to log in on both devices, sync through WeChat, download, then move it'' \\
    File size \& format caps (\texttimes\,7)
      & \small\itshape ``Discord has a file size limit; for anything larger I use Google Drive'' \\
    \rowcolor{cprimary!8}
    Cloud storage quota exhaustion (\texttimes\,6)
      & \small\itshape ``I've already used 3 Google accounts worth of the free 15 GB'' \\
    Speed throttling behind paywall (\texttimes\,6)
      & \small\itshape ``Cloud storage requires a paid membership for full speed'' \\
    \rowcolor{cprimary!8}
    WeChat save-location friction (\texttimes\,4)
      & \small\itshape ``WeChat automatically saves files somewhere weird; you have to Save As every time'' \\
    \bottomrule
  \end{tabularx}
  \vspace{0.3em}
  {\footnotesize \texttimes{} = affinity map tally; all findings supported by $\geq$2 interviewees.}
\end{frame}
\section{Value Proposition}
 
\begin{frame}[shrink=12]{Value Proposition}
  \begin{block}{}
    \centering\itshape\small
    For multi-device users who lose files to interruptions and platform walls,\\[0.1em]
    \textbf{Envoix} automatically routes every transfer via the fastest available
    path --- LAN, P2P, or relay --- with uniform end-to-end encryption,
    no account, no size cap, and no speed throttle.
  \end{block}
  \vspace{0.2em}
  \small
  \renewcommand{\arraystretch}{1.1}
  \begin{tabular}{p{4.8cm} p{7.2cm}}
    \toprule
    \textbf{Pain Point (\texttimes)} & \textbf{How Envoix Addresses It} \\
    \midrule
    Interrupted; no auto-resume (11)
      & Built-in resumable transfer; reconnects silently after any network drop \\
    Cross-platform wall (7)
      & Runs on iOS, Android, Windows, macOS, Linux --- one app, zero friction \\
    File size \& format caps (7)
      & No server storage; size bounded only by local disk \\
    Storage quota \& speed throttle (6)
      & LAN direct path at full NIC speed; relay is ciphertext-only fallback \\
    Privacy resignation (6)
      & E2EE before leaving the device; relay never sees plaintext \\
    \bottomrule
  \end{tabular}
\end{frame}
 
% ---- Storyboard ----
\begin{frame}{Storyboard --- ``Lin's 11 PM Deadline''}
  \scriptsize
  \setlength{\tabcolsep}{3pt}
  \renewcommand{\arraystretch}{1.0}
  \begin{tabular}{|p{3.72cm}|p{3.72cm}|p{3.72cm}|}
    \hline
    \cellcolor{red!8}
    \textbf{1 · The Deadline}\newline\vspace{0.1em}
    Lin is finishing her design project at 11 PM.
    She needs to send a 2 GB video render to her
    Windows teammate before midnight.\newline
    \textit{\faExclamationTriangle~Rushed, under pressure}
    &
    \cellcolor{red!15}
    \textbf{2 · Three Tools Fail}\newline\vspace{0.1em}
    AirDrop: ``Apple only.''
    Discord: file too large.
    WeChat: starts, then drops with no resume.
    15 minutes wasted.\newline
    \textit{\faFrown~Frustrated, helpless}
    &
    \cellcolor{yellow!15}
    \textbf{3 · Opens Envoix}\newline\vspace{0.1em}
    Teammate suggests Envoix.
    She opens it --- no sign-up screen.
    ``Send File'' is the first thing she sees.\newline
    \textit{\faSmile~Cautiously hopeful}
    \\
    \hline
    \cellcolor{yellow!8}
    \textbf{4 · One Scan to Pair}\newline\vspace{0.1em}
    Teammate shows a QR code on his screen.
    She scans it.
    Devices paired in under 2 seconds.
    She taps the file and hits Send.\newline
    \textit{\faSurprise~Surprised by simplicity}
    &
    \cellcolor{green!10}
    \textbf{5 · LAN Direct Transfer}\newline\vspace{0.1em}
    Envoix detects both are on the same Wi-Fi.
    Routes directly over LAN --- no cloud, no relay.
    2 GB transferred in 40 seconds at full speed.\newline
    \textit{\faStar~Pleasantly astonished}
    &
    \cellcolor{green!20}
    \textbf{6 · File Received, Deadline Met}\newline\vspace{0.1em}
    File arrives intact, original quality.
    ``That was it?''
    Project submitted on time --- no cloud, no drama.\newline
    \textit{\faHeart~Relieved and delighted}
    \\
    \hline
  \end{tabular}
  \vspace{0.25em}
  {\footnotesize\textbf{Pain points resolved:} interruption (\texttimes11) · cross-platform wall (\texttimes7) · file size cap (\texttimes7)}
  \hfill
  {\footnotesize\itshape % TODO: replace cells with illustrated panels from storyboardthat.com
  }
\end{frame}

% ================================================================
\section{Competitor Analysis}
% ================================================================

\begin{frame}{Market Overview}
  \begin{block}{The Fundamental Gap}
    Existing systems typically optimize for \textbf{exactly one transport pathway}. No single consumer app combines all approaches into a unified, adaptive experience.
  \end{block}

  \vspace{0.5em}

  \begin{columns}[c]
    \column{0.2\textwidth}
    \centering\small\textbf{Cloud Storage}\\[0.3em]
    \footnotesize Google Drive\\iCloud · Dropbox
    \column{0.2\textwidth}
    \centering\small\textbf{Messaging Apps}\\[0.3em]
    \footnotesize WeChat\\WhatsApp · Telegram
    \column{0.2\textwidth}
    \centering\small\textbf{LAN}\\[0.3em]
    \footnotesize AirDrop\\Nearby Share
    \column{0.2\textwidth}
    \centering\small\textbf{Internet P2P}\\[0.3em]
    \footnotesize BitTorrent\\Syncthing
    \column{0.2\textwidth}
    \centering\small\textbf{PAKE Transfer}\\[0.3em]
    \footnotesize Magic Wormhole\\croc
  \end{columns}

  \vspace{0.8em}
  \centering\textbf{Competitors analyzed:} Google Drive · WeChat · AirDrop · BitTorrent · croc
\end{frame}

\begin{frame}{Competitor Profiles (1/2)}

\vspace{-1.2em}

\footnotesize
\setlength{\itemsep}{0em}
\linespread{0.9}\selectfont

\begin{columns}[t]

\column{0.48\textwidth}

\begin{block}{Google Drive --- Cloud Storage}
\begin{itemize}
  \item[\faPlus] Persistent storage
  \item[\faPlus] Cross-device sync
  \item[\faPlus] 15 GB free storage
  \item[\faPlus] No recipient installation
  \item[\faPlus] Fast transfer
  \item[\faMinus] Double bandwidth usage
  \item[\faMinus] Metadata leakage
  \item[\faMinus] Subscription pressure
  \item[\faMinus] Poor for transient transfer
  \item[\faMinus] Privacy concerns
\end{itemize}
\end{block}

\column{0.48\textwidth}

\begin{block}{WeChat --- Messaging App}
\begin{itemize}
  \item[\faPlus] 1.3B+ users
  \item[\faPlus] Already widely used
  \item[\faPlus] Fast and convenient
  \item[\faMinus] 1 GB file limit
  \item[\faMinus] Aggressive compression
  \item[\faMinus] Multiple local copies
  \item[\faMinus] No persistent storage
  \item[\faMinus] Ecosystem lock-in
  \item[\faMinus] Surveillance/privacy risks
\end{itemize}
\end{block}

\end{columns}
\end{frame}

\begin{frame}{Competitor Profiles (2/2)}

\vspace{-2.0em}

\small
\setlength{\itemsep}{0em}
\linespread{0.9}\selectfont
\begin{columns}[t]

\column{0.34\textwidth}

\begin{block}{AirDrop --- LAN}
\begin{itemize}
  \item[\faPlus] Bluetooth + Wi-Fi Direct
  \item[\faPlus] No account required
  \item[\faPlus] No internet required
  \item[\faPlus] Seamless Apple UX
  \item[\faMinus] Apple-only
  \item[\faMinus] Proximity-only
  \item[\faMinus] No remote fallback
  \item[\faMinus] Discovery may leak info
\end{itemize}
\end{block}

\column{0.33\textwidth}

\begin{block}{BitTorrent --- Internet P2P}
\begin{itemize}
  \item[\faPlus] Cross-platform
  \item[\faPlus] Widely used
  \item[\faPlus] Fast P2P transfer
  \item[\faPlus] Secure transfer
  \item[\faMinus] Optimized for many peers
  \item[\faMinus] Weak in small networks
\end{itemize}
\end{block}

\column{0.33\textwidth}

\begin{block}{croc --- PAKE Transfer}
\begin{itemize}
  \item[\faPlus] SPAKE2 cryptographic model
  \item[\faPlus] Relay stores no plaintext
  \item[\faPlus] Resistant to offline attack
  \item[\faPlus] Open-source
  \item[\faPlus] Closest arch to Envoix
  \item[\faMinus] Desktop CLI-only
  \item[\faMinus] No LAN fast path
  \item[\faMinus] All traffic via relay
\end{itemize}
\end{block}

\end{columns}

\end{frame}


\linespread{1.0}\selectfont
\small
\begin{frame}{Comparison Table}

\vspace{-0.5em}

\scriptsize
\linespread{0.95}\selectfont

\centering

\resizebox{\textwidth}{!}{%
\begin{tabular}{lcccccc}
\toprule
\textbf{Feature} &
\textbf{Google Drive} &
\textbf{WeChat} &
\textbf{AirDrop} &
\textbf{BitTorrent} &
\textbf{croc} &
\textbf{Envoix} \\
\midrule

Cross-platform
& \checkmark
& Partial
& $\times$
& \checkmark
& \checkmark
& \textbf{\checkmark} \\

LAN / local transfer
& $\times$
& $\times$
& \checkmark
& $\times$
& $\times$
& \textbf{\checkmark} \\

Internet / relay
& \checkmark
& \checkmark
& $\times$
& $\times$
& \checkmark
& \textbf{\checkmark} \\

P2P transfer
& $\times$
& $\times$
& \checkmark
& \checkmark
& $\times$
& \textbf{\checkmark} \\

\rowcolor{cprimary!15}
Auto-routing
& $\times$
& $\times$
& $\times$
& $\times$
& $\times$
& \textbf{\checkmark} \\

\rowcolor{cprimary!15}
Adaptive LAN + relay
& $\times$
& $\times$
& $\times$
& $\times$
& $\times$
& \textbf{\checkmark} \\

\rowcolor{cprimary!15}
E2EE (all modes)
& $\times$
& $\times$
& Partial
& Partial
& \checkmark
& \textbf{\checkmark} \\

No account required
& \checkmark
& $\times$
& \checkmark
& \checkmark
& \checkmark
& \textbf{\checkmark} \\

No ecosystem lock-in
& \checkmark
& $\times$
& $\times$
& \checkmark
& \checkmark
& \textbf{\checkmark} \\

Mobile app
& \checkmark
& \checkmark
& \checkmark
& Partial
& $\times$
& \textbf{\checkmark} \\

Resume on failure
& Partial
& $\times$
& $\times$
& Partial
& $\times$
& \textbf{\checkmark} \\

Open-source
& $\times$
& $\times$
& $\times$
& \checkmark
& \checkmark
& \textbf{\checkmark} \\

\bottomrule
\end{tabular}%
}

\end{frame}

% ================================================================
% Closing
% ================================================================

\appendix
% \section{User Interview Questionnaire}

\begin{frame}[shrink=8]{Interview Design --- Participants \& Venue}
  \begin{columns}[t]
    \column{0.5\textwidth}
    \begin{block}{How We Find Interviewees}
      \begin{itemize}
        \item SJTU engineering/CS communities
        \item GitHub discussions, V2EX, WeChat tech groups
        \item Screening: regularly transfer files across multiple devices/OS, and have encountered at least one of: size limits, incompatibility, network failure, privacy concerns
        \item \textbf{Avoid friends/family} --- reduce social desirability bias
      \end{itemize}
    \end{block}
    \column{0.5\textwidth}
    \begin{block}{Venue \& Session Structure}
      \begin{itemize}
        \item Remote via Tencent Meeting / Zoom
        \item 10--20 min per session
        \item One interviewer + one note-taker
        \item Recorded with consent
      \end{itemize}
      \vspace{0.5em}
      \begin{tabular}{ll}
        0--5 min  & Warm-up, device context \\
        5--15 min & Pain stories, failure scenarios \\
        15--20 min & Ideal workflow, retention \\
      \end{tabular}
    \end{block}
  \end{columns}
\end{frame}

\begin{frame}{Theme 1: Device Context \& Current Behavior}
  \textit{Goal: Establish devices/platforms used and current tools, without leading toward any product concept.}

  \vspace{0.8em}

  \begin{enumerate}
    \item[\textbf{Q1}] Walk me through the devices you use daily and how often they need to share files with each other.
    \item[\textbf{Q2}] Think back to the last few weeks --- what triggered your need to send a file, and to whom?
    \item[\textbf{Q3}] What apps or methods do you normally reach for? How did you settle on those tools?
    \item[\textbf{Q4}] When you're about to send a file, what goes through your head before deciding which tool to use?
  \end{enumerate}
\end{frame}

\begin{frame}{Theme 2: Pain Points \& Failure Stories}
  \textit{Goal: Surface real breakdown moments, workarounds, and emotional friction.}

  \vspace{0.8em}

  \begin{enumerate}
    \item[\textbf{Q5}] Walk me through the last time you sent a large file --- from the moment you decided to send it to delivery.
    \item[\textbf{Q6}] Has your usual method ever just stopped working? What happened, and what did you do instead?
    \item[\textbf{Q7}] When transferring between iPhone and Android, or phone and a different-OS computer, how do you handle that?
    \item[\textbf{Q8}] Describe a time when security/privacy crossed your mind during a file transfer. Did it change your behavior?
    \item[\textbf{Q9}] What does it feel like when a transfer fails or arrives corrupted? Tell me about a specific moment.
  \end{enumerate}
\end{frame}

\begin{frame}{Theme 3: Motivations, Ideals \& Accepted Friction}
  \textit{Goal: Understand retention drivers, unarticulated needs, and normalized workarounds.}

  \vspace{0.8em}

  \begin{enumerate}
    \item[\textbf{Q10}] When a file transfer tool works really well, what makes you keep coming back to it?
    \item[\textbf{Q11}] Describe your ideal file-sending experience for a scenario that comes up regularly for you.
    \item[\textbf{Q12}] What frustrations have you accepted as ``the way file transfer works'' --- things you've stopped trying to fix?
  \end{enumerate}
\end{frame}
\author{}
\title{}
\renewcommand{\bottomthanks}{\fontsize{52}{62}\selectfont\textbf{Thank You}}
\makebottom

\end{document}
